Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-06-28 code/paper.Rmd
stash

```{r}
# Histogram of proportion of anonymous edits 
# TODO and random sites
ggplot(revision_history_page_details_ip_addresses_countries,
       aes(prop_anon_of_all_edits)) +
  geom_histogram() +
  theme_minimal(base_size = 12) +
  xlab("Proportion of all edits that are anonymous")
```

>>>>

```{r}
# Histogram of proportion of anonymous edits 
# TODO and random sites
ggplot(revision_history_page_details_ip_addresses_countries,
       aes(prop_anon_of_all_edits)) +
  geom_histogram() +
  theme_minimal(base_size = 12) +
  xlab("Proportion of all edits that are anonymous")

ggsave("figures/wh_wikipedia_pages_anon_edits_prop.png")
```
